Randomly select papers for review

### 2021-11-30 R Code/Randomise_Papers.Rmd.Rmd
Added rankings

opts_knit$set(root.dir = "/Users/kelleherj/Documents/Research/QAEco/ODM_Review/")
```

@@

```{r Randomly rank papers within strata}
rankedPapers <- paperList %>%
  # Add random ranks for all papers
  mutate(randRank = sample(x = 1:nrow(.), size = nrow(.))) %>%
  # Re-rank within strata
  group_by(Query, YearPeriod) %>%
  arrange(Query, YearPeriod, randRank) %>%
  mutate(groupRank = row_number())

```

>>>>

opts_knit$set(root.dir = "/Users/kelleherj/Documents/Research/QAEco/ODM_Review/dynamic-occupancy-model-review/")
```

@@

```{r Randomly rank papers within strata}
rankedPapers <- paperList %>%
  # Add random ranks for all papers
  mutate(randRank = sample(x = 1:nrow(.), size = nrow(.))) %>%
  # Re-rank within strata
  group_by(Query, YearPeriod) %>%
  arrange(Query, YearPeriod, randRank) %>%
  mutate(GroupRank = row_number()) 
```

```{r Highlight papers to read}
# Identify which papers qualify to be read
highlightedPapers <- rankedPapers %>%
  group_by(Query, YearPeriod) %>%
  mutate(PercentRank =  GroupRank/max(GroupRank)) %>%
  mutate(ToRead = case_when(
    # If there are fewer than 5, read them all
    max(GroupRank) <= 5 ~ "YES",
    # If there are 20 or fewer, read the top 5
    max(GroupRank) <= 20 & GroupRank <= 5 ~ "YES",
    max(GroupRank) <= 20 & GroupRank >= 5 ~ "NO",
    # If there are 21 or more, read the top 25%
    max(GroupRank) >= 21 & PercentRank <= 0.25  ~ "YES",
    max(GroupRank) >= 21 & PercentRank > 0.25 ~ "NO")) %>%
  ungroup() %>%
  # Get Review_ID, GroupRank, and ToRead
  select(Review_ID, GroupRank, ToRead)

# Write to disk
write_csv(highlightedPapers, file = "RankedPapers.csv")
```
